---
title       : Interactive classification of Iris Species
subtitle    : Using tree based algorithms
author      : Subroto Datta
job         : Coursera Data Products
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : standalone # {selfcontained, standalone, draft}
knit        : slidify::knit2slides
---

## Interactive application of Predicting Iris species

1. Used to classify one of three Iris plant species setosa, virginica, versiflower.
2. Based on flower sepal and petal measurements in centimeters
3. Provides a choice of two classification models.
4. Models were trained against Ronald Fisher's <a href="https://en.wikipedia.org/wiki/Iris_flower_data_set">iris flower dataset</a> available in base R.
5. User enters 4 measurements and receives a prediction.

<br>
<br>

The two classification models are based on the following algorithms

1. <b> randomForest </b> which is a tree based predictor based on bootstrapped aggregation.
2. <b> rpart </b> Regression Partitioning and Decision Tree


Description for using these two algorithms with R are available <a href="http://www.statmethods.net/advstats/cart.html">here.</a>



--- .class #id 

## Descriptive statistics : Iris Data Set 

```{r, echo=FALSE}
data(iris)
head(iris, 1)
summary(iris)
```

--- .class #id 

## Pairs Plot : Iris Data Set 
```{r, echo=FALSE}
pairs(iris[1:4], main = "Iris Data", pch = 21, bg = c("red", "green3", "blue")[unclass(iris$Species)]) 
```

--- .class #id 

## Usage

1. The application is available <a href="https://subrotod.shinyapps.io/DDProject">here.</a>
2. The data is entered in <b>cms </b> in the left panel.
3. <b>Important </b> Press the Go! button to obtain the predictions on the input data.
4. The prediction is available in the Result panel. The two algorithms may give different predictions in some cases.
5. Refer to the Help panel for sample data.






